\cvsection{Experience}
\begin{cventries}
  \cventry
    {Software Engineering Intern}
    {Microsoft}
    {Online}
    {May. 2020 - Aug. 2020}
    {
      \begin{cvitems}
        \item{Developed a React Native library to replace a 3rd-party deprecated user feedback package.}
        \item{Collaborated with another intern throughout the development process, allowing for greater throughput via parallelizing tasks.}
        \item{Learned how to produce a feature-complete library, including localization, defensive design, documentation, and integration into existing products.}
        \item{Designed user feedback menus to increase engagement in posted requests and reduce the possibility of duplicate feature requests, decreasing the work required by the feedback support team.}
        \item{Created a continuous integration and deployment pipeline using Azure DevOps to handle code verification on Android and iOS platforms as well as package publishing.}
      \end{cvitems}
    }
  \cventry
    {Project Manager, Scrum Master, \& Developer}
    {Survey for Polysubstance Drug Abuse Study}
    {Gainesville, FL}
    {Jan. 2019 - Mar. 2020}
    {
      \begin{cvitems}
        \item {Developed Electron and React desktop application for collecting data on substance abuse for the UF College of Epidemiology.}
        \item {Acted as main communicator with the client Dr. Linda Cottler, Associate Dean of Research and Dean's Professor for UF's Colleges of Health and Medicine.}
        \item {Learned how to balance changing user requirements with the fixed deadline, granting the team flexibility while still pursuing a complete product.}
        \item {Delegated tasks to two other teammates using Agile practices, breaking down complex tasks into individually achievable portions.}
      \end{cvitems}
    }
  \cventry
    {Webmaster \& Website Developer}
    {Association of Computer Engineers}
    {Gainesville, FL}
    {Nov. 2019 - Feb. 2021}
    {
      \begin{cvitems}
        \item {Developed a web application using Ruby on Rails and React to facilitate club event and user management.}
        \item {Worked with elected board of club to produce client requirements and work items, focusing on increasing member engagement.}
        \item {Designed the website via the microservice approach, allowing for the independent scaling of all components of the web app.}
        \item {Verified operation with high test coverage and an automated continuous integration and publishing pipeline using Concourse CI.}
        \item {Opened website to open source collaboration with a well structured issues board and documentation.}
      \end{cvitems}
    }
\end{cventries}
